Draft Documents

### 2022-11-16 src/draft.Rmd
f4

###  3.3.2. Assessment
###  3.3.3. Interpretation

>>>>

###  3.3.2. Assessment
Assessment of linear model lm1: 
the predicted model has some NA values which are removed. The error rates are too high, therefore, this method of variable selection may not be suitable
```{r}
eval.metrics.linreg <- function(actual, predicted) {
  residual <- actual - predicted
  mse <- mean(residual ^ 2)
  mae <- mean(abs(residual))
  rmse <-  sqrt(mse)
  mape <- mean(abs(residual / actual)) * 100

  data.frame(
    MSE = mse,
    MAE = mae,
    RMSE = rmse,
    MAPE = mape
  )
}
predicted<-predict(lm1,newdata=test)
actual<-test$pov
df23<-na.omit(data.frame(actual,predicted))
ac<-df23$actual
pr<-df23$predicted
eval.metrics.linreg(ac,pr)
```
###  3.3.3. Interpretation
gdp per capital, income class and region of the country can provide a model to predict the poverty headcount ratio in a country.
